Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2019-11-21 doc/Paper/main.tex
Fixed typo.

  Despite the small fraction of sky covered by the data used in this work, HSC DR1 constitutes an ideal proxy for the data expected for LSST. Our analysis demonstrates the feasibility of photometric galaxy clustering studies using such high signal-to-noise datasets. In particular, this work shows the level of readiness of the LSST DESC analysis pipelines, and showcases the application of power spectrum methods for galaxy clustering, and the use of template deprojection techniques to handle contamination from sky systematics. We anticipate that future development of this pipeline will include improvements to photo-z marginalization and non-linear bias modeling, thus permitting its application to magnitude-limited galaxy samples with even higher signal-to-noise. These results therefore bode well for future cosmological constraints using galaxy clustering data from LSST.

>>>>

  Despite the small fraction of sky covered by the data used in this work, HSC DR1 constitutes an ideal proxy for the data expected for LSST. Our analysis demonstrates the feasibility of photometric galaxy clustering studies using such high signal-to-noise datasets. In particular, this work shows the level of readiness of the LSST DESC analysis pipelines, and showcases the application of power spectrum methods for galaxy clustering, and the use of template deprojection techniques to handle contamination from sky systematics. We anticipate that future development of this pipeline will include improvements to photo-$z$ marginalization and non-linear bias modeling, thus permitting its application to magnitude-limited galaxy samples with even higher signal-to-noise. These results therefore bode well for future cosmological constraints using galaxy clustering data from LSST.
